---
title: "a3_task4_cali_pfleger"
author: "Cali Pfleger"
date: "10/30/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
library(kableExtra)
library(lubridate)
library(car)
```


```{r}
urchins <- read_csv(here("data", "urchins.csv")) %>% 
  clean_names() 
```

## a) Wrangle Urchin data to only include Purple Urchin Data from January (1) 2010
```{r}
urchins_2010 <-urchins %>% 
  filter(common_name %in% c("Purple Urchin")) %>% 
  filter(site %in% c("NAPL")) %>% 
   mutate(date= mdy(date)) %>% 
  mutate(year = year(date)) %>% 
  filter(year == 2010) %>% 
  mutate(month= month(date)) %>% 
  filter(month == 1)


```


## b) Mean group_by(treatment) %>% 
  
```{r}
urchins_2010 %>% 
  ggplot(aes(x = size)) +
  geom_histogram(bins = 15) +
  facet_wrap(~treatment)

urchins_2010 %>% 
  ggplot(aes(sample = size)) +
  geom_qq() +
  facet_wrap(~treatment)
```
## b) Main takeaways
- I do no think that there is a large variance in the difference in sizes between the annual and control groups. 

##  c) Create a table of desciptive stats

```{r}
urchins_stats <- urchins_2010 %>% 
  group_by(treatment) %>% 
  summarise(mean_urchins =mean (size),
            median_urchins = median(size),
            sd_urchins = sd(size),
            n = n()) #calculate number of observations in each group )

kbl(urchins_stats)
```

## d) Two-sample t-test to compare means between the two groups

```{r}
annual_urchins <- urchins_2010 %>% 
  filter(treatment == ("ANNUAL")) %>% 
  pull(size)

control_urchins <- urchins_2010 %>% 
  filter(treatment == ("CONTROL")) %>% 
  pull(size)


t.test(x= annual_urchins, y= control_urchins)

```
## e) Comparing the means statement 
-  The mean of the annual urchin data is 3.92 and the mean of the control urchin data is 3.73, which is a difference in 0.190864. The calculated standard deviation (sd) for the annual urchins is .~9 and the sd for the control urchins is ~8.6, which is about 1/3 of the mean size for both groups. 

The p-value of 0.2536 means that there is a 25% chance that these data could have been randomly sampled.

## f) The Meaning of the p-value from the t-test above

- The two sample t-test between annual and control urchins in January 2010 resulted in a p-value of 0.2536 which means that there is a ~25% chance that the difference between the size of the two groups is due to random collection error. 




