---
title: "a3-task3-task4"
author: "Cali Pfleger"
date: "10/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
library(kableExtra)
library(lubridate)
```

## Read in urchins data 

```{r}
urchins <- read_csv(here("data", "urchins.csv")) %>% 
  clean_names() 
```


## Section 1: Exploratory Data Vizualization
- i: Size comparsison between purple and red urchins using data from all sites and both treatments shown by histogram 


```{r}
urchins_size <-urchins %>% 
  filter(common_name %in% c("Red Urchin", "Purple Urchin")) 
  ggplot(data = urchins_size, aes(x = size)) +
  geom_histogram(bins= 15) +
  facet_wrap(~common_name)
```



## Section 1: Exploratory Data Vizualization
i: Size comparison between purple and red urchins using data from all sites and both treatments shown by boxplot

```{r}
urchins_size <-urchins %>% 
  filter(common_name %in% c("Red Urchin", "Purple Urchin")) 
  ggplot(data = urchins_size) +
    geom_boxplot(aes(x= common_name, y= size))
  
```


## Section 1: Descriptive Statistics Table

ii: Summary table for purple and red urchins -> mean, median, SD, and sample size 


```{r}
urchins_stats <- urchins %>% 
  group_by(common_name) %>% 
  summarise(mean_urchins =mean (size),
            median_urchins = median(size),
            sd_urchins = sd(size),
            n = n()) #calculate number of observations in each group )

kbl(urchins_stats)
```


## Section 1: Overall takeaways

- Purple urchins are more 




## Section 2:Explore purple urchin counts by site and year
- i 
```{r}
purple_urchins <- urchins %>% 
  filter(common_name %in% c("Purple Urchin")) %>% 
  mutate(date= mdy(date)) %>% 
  mutate(year = year(date)) %>%  #new column that only has year 
  mutate(site_full = case_when(
    site %in% c("NAPL") ~ "Naples Reef",
    site %in% c("AQUE") ~ "Arroyo Quemado Reef",
    site %in% c("CARP") ~ "Carpinteria Reef",
    site %in% c("MOHK") ~ "Mohawk Reef",
    site %in% c("IVEE") ~ "Isla Vista Reef"
    
  ))
 
```


## Section 2:Explore purple urchin counts by site and year
- ii make a summary table with the total # of purple urchins observed by site and year 

```{r}

```











